Run-Time Monitoring with Adjustable Overhead \\Using Dataflow-Guided Filtering

### 2015-01-05 policies.tex
Revised throughout.

An alternative dropping policy which eliminates this wasted work is to only
make dropping decisions at the root or source of these metadata flows (see Figure~\ref{fig:policies.source_drop}). That is,
we will decide to either monitor or not monitor an entire metadata flow. An
example of these source nodes is the monitoring done to initialize base and
bounds information on {\tt malloc} for an array bounds check. These source
nodes are typically easy to identify by the dropping hardware because they
correspond to the special instructions that are used to set up metadata
information. Thus, it is not necessary to generate and analyze the monitoring
dependence graph to identify source nodes. We refer to this dropping decision
policy as \emph{source-only
dropping} and we refer to the previous policy of dropping any event as
\emph{unrestricted dropping}.

More complex dropping policies can be implemented given more detailed
information about the monitoring dependence graph. Here, we describe one such
policy, which we call \emph{sub-flow dropping}. Sub-flow dropping makes
dropping decisions at a granularity in between unrestricted dropping and
source-only dropping (see Figure~\ref{fig:policies.subflow_drop}). Sub-flow
dropping allows source nodes to be dropped and nodes after branch points in the
monitoring dependence graph to be dropped. From
Figure~\ref{fig:policies.subflow_drop}, this corresponds to nodes {\tt A}, {\tt
C}, and {\tt F}. The basic idea of sub-flow dropping is to drop portions of the
monitoring dependence graph at the smallest granularity such that no work is
wasted.
For example,
dropping node {\tt C} causes nodes {\tt D} and {\tt E} to be skipped. However,
performing monitoring on the remaining nodes allows the check at node {\tt G}
to be performed with no wasted work. Similarly, dropping {\tt F} allows node
{\tt E} to be checked with no wasted work.

%Figures~\ref{fig:policies.all_drop} and \ref{fig:policies.source_drop} show a
%comparison of where dropping decisions are made for these two policies. 
Source-only dropping will
result in no wasted work and thus better coverage at a given overhead than unrestricted dropping. However, because of the coarser-grained decision, it
may be more difficult to closely match overhead targets. 
Sub-flow dropping enables a design point in between unrestricted dropping and
source-only dropping in terms of matching overhead and coverage achieved.
Sub-flow dropping can still result in wasted work in there are merge points in
the monitoring dependence graph, but should result in less wasted work than
unrestricted dropping. Thus, its coverage falls in between that of source-only dropping and unrestricted dropping. Similarly, sub-flow dropping's ability to closely match overhead targets falls between that of source-only dropping and unrestricted dropping.
We expect source-only dropping 
to work well when there are a large number of independent metadata flows.
In addition, using a probabilistic dropping policy works poorly with
unrestricted dropping. Since every event in a dependent chain (e.g., events {\tt
A} through {\tt E}) needs to be monitored in order for the monitoring check to
be useful, randomly dropping any event is likely to cause the final check to be
invalid by dropping at least one event in the chain.

Depending on the target application of partial monitoring, different policies
are more applicable.
For applications where closely matching an overhead target is important, a
slack-based, unrestricted dropping policy is appropriate. However, if matching
the overhead target is not as important, then a slack-based, sub-flow or source-only dropping
policy could provide better coverage. 
Finally, if the goal is to use partial monitoring to enable cooperative
debugging and testing with very low overhead, then a probabilistic,
source-only dropping policy can be used to provide good total coverage over
multiple runs.
For a probabilistic policy, sub-flow dropping allows better overhead matching than source-only dropping
while still allowing good total coverage over multiple runs, though at a slower
rate than source-only dropping.

>>>>

An alternative dropping policy which eliminates this wasted work is to only
make dropping decisions at the root or source of these metadata flows (see Figure~\ref{fig:policies.source_drop}). That is,
we will decide to either monitor or not monitor an entire metadata flow. An
example of these source nodes is the monitoring done to initialize base and
bounds information on {\tt malloc} for an array bounds check. These source
nodes are easily identifiable by the dropping hardware because they typically
correspond to the special instructions that are used to set up metadata
information. Thus, it is not necessary to generate and analyze the monitoring
dependence graph to identify source nodes. We refer to this dropping decision
policy as \emph{source-only
dropping} and we refer to the previous policy of dropping any event as
\emph{unrestricted dropping}.

More complex dropping policies can be implemented given more detailed
information about the monitoring dependence graph. This information can be
found through static analysis or profiling, though we do not explore how to
find it in detail here. Given this information, we describe one possible
policy to use it, which we call \emph{sub-flow dropping}. Sub-flow dropping makes
dropping decisions at a granularity in between unrestricted dropping and
source-only dropping (see Figure~\ref{fig:policies.subflow_drop}). 
The basic idea of sub-flow dropping is to drop portions of the monitoring
dependence graph at the smallest granularity such that no work is wasted.
Sub-flow dropping allows source nodes to be dropped and nodes after branch
points in the monitoring dependence graph to be dropped. From
Figure~\ref{fig:policies.subflow_drop}, this corresponds to nodes {\tt A}, {\tt
C}, and {\tt F}. For example,
dropping node {\tt C} causes nodes {\tt D} and {\tt E} to be skipped. However,
performing monitoring on the remaining nodes allows the check at node {\tt G}
to be performed with no wasted work. Similarly, dropping {\tt F} allows node
{\tt E} to be checked with no wasted work.

%Figures~\ref{fig:policies.all_drop} and \ref{fig:policies.source_drop} show a
%comparison of where dropping decisions are made for these two policies. 
Source-only dropping will
result in no wasted work and thus better coverage at a given overhead than unrestricted dropping. However, because of the coarser-grained decision, it
may be more difficult to closely match overhead targets. 
Sub-flow dropping enables a design point in between unrestricted dropping and
source-only dropping in terms of matching overhead and coverage achieved.
Sub-flow dropping can still result in wasted work if there are merge points in
the monitoring dependence graph and only one part of the incoming flows is
dropped, but should result in less wasted work than
unrestricted dropping. Thus, its coverage falls in between that of source-only
dropping and unrestricted dropping. Similarly, sub-flow dropping's ability to
closely match overhead targets falls between that of source-only dropping and
unrestricted dropping.
We expect source-only dropping 
to work well when there are a large number of independent metadata flows.
In addition, using a probabilistic dropping policy works poorly with
unrestricted dropping. Since every event in a dependent chain (e.g., events {\tt
A} through {\tt E}) needs to be monitored in order for the monitoring check to
be useful, randomly dropping any event is likely to cause the final check to be
invalid by dropping at least one event in the chain.

Depending on the target application of partial monitoring, different policies
are more applicable.
For applications where closely matching an overhead target is important, a
slack-based, unrestricted dropping policy is appropriate. However, if matching
the overhead target is not as important, then a slack-based, sub-flow or source-only dropping
policy could provide better coverage. 
Finally, if the goal is to use partial monitoring to enable cooperative
debugging and testing with very low overhead, then a probabilistic,
source-only or sub-flow dropping policy can be used to provide good total coverage over
multiple runs.

### 2015-01-05 related.tex
Revised throughout.

There exists a number of previous projects that have looked into performing
partial monitoring in order to reduce the performance overhead. These
platforms differ from ours in a number of ways including how monitoring is
implemented and the monitoring techniques targeted. However, we note three main
properties that differentiates our work:
\begin{enumerate}
  \item \textbf{Generality:} Our architecture applies to a variety of monitoring techniques.
  \item \textbf{Adjustable Overhead:} Our architecture allows an overhead to be
  targeted. Other work performs sampling to reduce overhead but does not try
  to bound overhead, which we have shown can vary greatly.
  \item \textbf{Prevent False Positives:} We prevent a mechanism to prevent
  false positives. Previous work either has false positives or targets monitoring
  techniques which degrade gracefully with sampling rather than exhibit false
  positives.
\end{enumerate}
Our work is the first that we know of to present a hardware platform for partial
monitoring that is general, allows an overhead target to be specified, and
explicitly prevents false positives. In contrast, previous work on
partial monitoring achieves only some, but not all, of these properties.
Table~\ref{tab:monitoring.previous_sampling} summarizes these differences.

@@

There also exists several projects that have looked into more general partial
monitoring platforms. Arnold and Ryder \cite{arnold-pldi01} presented a general
platform for sampling of instrumented code, but do not allow an overhead target
to be specified and do not prevent false positives. Huang et al.
\cite{huang-sttt12} proposed a general framework for controlling the overhead
of software-based monitoring. However, they also do not explicitly address
false positives and only target monitors which degrade gracefully when
performed partially. Lo et al. \cite{lo-rtas14} designed a hardware
architecture for performing monitoring on hard real-time systems that also
prevents false positives. Their architecture is designed to meet real-time
deadlines rather than overhead targets. In addition, in order to give strong
guarantees, the coverage achieved is lower than our system. Finally, QVM
\cite{qvm-oopsla08} proposes a modification to the Java Virtual Machine (JVM) to
support monitoring with adjustable overhead. QVM does prevent false positives
but does so by enabling or disabling monitoring on a per-object basis. This is
similar to the idea of performing source-only dropping which our results show
can lead to overshooting the overhead target depending on the monitoring
technique. In addition, QVM is limited monitoring for code run on a JVM while
our framework works for any binary.

>>>>

There exists a number of previous projects that have looked into performing
partial monitoring in order to reduce the performance overhead. These
platforms differ from ours in a number of ways including how monitoring is
implemented and the monitoring techniques targeted. However, we note three main
properties that differentiates our work:
\begin{enumerate}
  \item \textbf{Generality:} Our architecture applies to a variety of monitoring techniques.
  \item \textbf{Adjustable Overhead:} Our architecture allows an overhead to be
  targeted. Other work performs sampling to reduce overhead but does not try
  to bound overhead, which we have shown can vary greatly.
  \item \textbf{Prevent False Positives:} We present a mechanism to prevent
  false positives. Previous work either has false positives or targets monitoring
  techniques which degrade gracefully with sampling rather than exhibit false
  positives.
\end{enumerate}
Our work is the first that we know of to present a hardware platform for partial
monitoring that is general, allows an overhead target to be specified, and
explicitly prevents false positives. In contrast, previous work on
partial monitoring achieves only some, but not all, of these properties.
Table~\ref{tab:monitoring.previous_sampling} summarizes these differences.

@@

There also exists several projects that have looked into more general partial
monitoring platforms. Arnold and Ryder \cite{arnold-pldi01} presented a general
platform for sampling of instrumented code, but do not allow an overhead target
to be specified and do not prevent false positives. Huang et al.
\cite{huang-sttt12} proposed a general framework for controlling the overhead
of software-based monitoring. However, they also do not explicitly address
false positives and only target monitors which degrade gracefully when
performed partially. Lo et al. \cite{lo-rtas14} designed a hardware
architecture for performing monitoring on hard real-time systems that also
prevents false positives. Their architecture is designed to meet real-time
deadlines rather than enable adjustable overheads. In addition, in order to give strong
guarantees, the coverage achieved is lower than our system. Finally, QVM
\cite{qvm-oopsla08} proposes a modification to the Java Virtual Machine (JVM) to
support monitoring with adjustable overhead. 
QVM is limited to monitoring for code run on a JVM which limits its
generalizability while our framework works for any binary. QVM prevents false
positives by enabling or disabling monitoring on a per-object basis. This
limits the monitoring schemes that can be implemented. Also, this method of
preventing false positives is similar to the idea of performing source-only
dropping which our results show can lead to overshooting the overhead target
depending on the monitoring technique.
